Comparison of Catalogs

### 2024-07-24 compare/compare.qmd
fixed a26

ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
inc_corr = round(compare_data(dt["inc"], dt["INCL"], sigma = True)[3], 3)
a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"], sigma =True)[3], 3)
```

|      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:------------------:|:----------------:|
|     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |           INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |

As we can see we don't have any significant correlation between the Types of galaxies

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"], sigma =True)
scatter_plot(dt["a26_1"], dt["A26_1a"], yerr = dt["E_V"])

**For the A26: In the LCV Catalog it is measured in deg, and in Hecate it is mesaured in kpc**

## Luminosities

@@

|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
|:--------------:|:--------------:|:--------------:|:----------------------:|
| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:--------------:|:--------------:|:------------------------:|:--------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

|  LCV   |   HECATE   |                           Description                            |                  Count                  |
|:--------------:|:--------------:|:------------------------:|:--------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |

@@

|      LCV       |  HECATE  |                        Description                        |                  Count                  |
|:------------------:|:------------------:|:------------------------------:|:------------------------------:|
|     logM26     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logM26"]`     |
|     logMHI     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logMHI"]`     |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       | `{python} non_nan_counts["logM_HEC"]`   |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] | `{python} non_nan_counts["logM_GSW"]`   |
| logStellarMass |          |                Stellar Mass from M_*/L=0.6                | `{python} non_nan_counts["logStellarMass"]` |

@@

# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```

:::

>>>>

ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
inc_corr = round(compare_data(dt["inc"], dt["INCL"], sigma = True)[3], 3)
a26_corr = round(compare_data(dt["a26_1"], dt["R1"], sigma =False)[3], 3)
```

|      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:-----------------:|:----------------:|
|     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |           INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |

As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
scatter_plot(dt["a26_1"], dt["R1"])

```
## Luminosities

@@

|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:----------------:|:-----------------:|
| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:------------------:|:----------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

|  LCV   |   HECATE   |                           Description                            |                  Count                  |
|:----------------:|:----------------:|:------------------:|:----------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |

@@

|      LCV       |  HECATE  |                        Description                        |                    Count                    |
|:----------------:|:----------------:|:----------------:|:----------------:|
|     logM26     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logM26"]`     |
|     logMHI     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logMHI"]`     |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |    `{python} non_nan_counts["logM_HEC"]`    |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
| logStellarMass |          |               Stellar Mass from M\_\*/L=0.6               | `{python} non_nan_counts["logStellarMass"]` |

@@

# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```
:::

# Morphology
